\tool: Revisiting BadUSB with Type-C

### 2021-03-20 WOOT/Files/conclusion.tex
revise responsible disclosure.

\section{Responsible Disclosure}
Responsible disclosure have already been carried out, we have already contacted HUAWEI and Apple through proper channel. We received response from HUAWEI on \nth{7} March and discussed about the mitigation plan on \nth{10} March while Apple has not responded yet. HUAWEI security team has confirmed this issue and been weighing different mitigation approaches. We are actively facilitating their mitigating process and waiting for mitigation to be deployed. After the mitigation is deployed, HUAWEI will apply a CVE ID for this vulnerability.

>>>>

\section{Responsible Disclosure}
Responsible disclosure have already been carried out, we have contacted HUAWEI and Apple through proper channels. We received response from HUAWEI on March \nth{7} and discussed the mitigation plan on March \nth{10} while Apple has not responded yet. HUAWEI security team has confirmed this issue and been working on mitigation. We are actively facilitating their mitigation process and waiting for a fix to be deployed. After the mitigation is deployed, HUAWEI will assign a CVE ID for this vulnerability.
